Supplementary Material for Asymmetry paper

### 2020-05-14 Supplementary/Sup_mat.Rmd
added some description to the power analysis for 2.2

```{r firetruck-data, include = T, fig.height = 3, echo = F, fig.align = 'center', fig.cap="_boxplots for the empirical data being sampled from._"}
# so we're interested in the difference between the closest and furthest... 
# so we should just plot that? 
load("../power/Money_and_two/scratch/df_sample")
load("../power/Money_and_two/scratch/df_all")
plt_data <- df_all %>%
  filter(standard_lab %in% c("10%","90%")) %>%
  group_by(participant, condition, standard_lab) %>% 
  summarise(norm_pos = mean(norm_pos)) %>%
  ggplot(aes(standard_lab, norm_pos,
             colour = condition,
             fill = condition)) + 
  geom_boxplot(alpha = .3) + 
  geom_point(alpha = .3, position = position_jitterdodge(.1)) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  theme_bw() +
  scale_y_continuous("Normalised Placement") +
  theme(axis.title.x = element_blank()) + 
  guides(colour = guide_legend(title = "Condition"),
         fill = guide_legend(title = "Condition"))

@@

plt_data_diff
```

To perform our power analysis we ....

>>>>

```{r firetruck-data, include = T, fig.height = 3, echo = F, fig.align = 'center', fig.cap="_boxplots for the empirical data being sampled from._"}
# so we're interested in the difference between the closest and furthest... 
# so we should just plot that?

# load data
load("../power/Money_and_two/scratch/df_sample")
load("../power/Money_and_two/scratch/df_all")

# make plot 
plt_data <- df_all %>%
  filter(standard_lab %in% c("10%","90%")) %>%
  group_by(participant, condition, standard_lab) %>% 
  summarise(norm_pos = mean(norm_pos)) %>%
  ggplot(aes(standard_lab, norm_pos,
             colour = condition,
             fill = condition)) + 
  geom_boxplot(alpha = .3) + 
  geom_point(alpha = .3, position = position_jitterdodge(.1)) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  theme_bw() +
  scale_y_continuous("Normalised Placement") +
  theme(axis.title.x = element_blank()) + 
  guides(colour = guide_legend(title = "Condition"),
         fill = guide_legend(title = "Condition"))

@@

plt_data
```

To perform our power analysis we sampled these datasets 5000 times for a range of participants ($N = 2...28$). To do this, N participants were chosen at random (with replacement) from each condition (i.e. the _Throwing_ or _Avatar_ "conditions"), then 60 data points were sampled from each of these participants (with replacement) for the closest ("90%") and furthest separations ("10%").
